---
title: "Intro"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Intro}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Installing instaloader

Load library

```{r example}
library(instr)

```

Install instaloader and python: 

```{r, eval = F}
instr::install_instaloader()
```

```{r, eval=F}
instr::init_instr()
```

### Get Posts with Hashtag

Return a tibble with 10 Instagram posts that use `#coronavirus`.


```{r, eval = F}
covid <- insta_posts(query = "covid", 
                         scope = "hashtag",
                         max_posts = 3, 
                         scrape_comments = F)

head(covid)

```

### Get Posts from a Specific User

Return a tibble with the 5 Instagram posts by `francediplo`.

```{r, eval = F}
francediplo <- insta_posts(query = "francediplo", 
                         scope = "username",
                         max_posts = 3, 
                         scrape_comments = F)

francediplo
```

Return a tibble with the 5 Instagram posts by `francediplo`.

```{r, eval = F}
francediplo_comments <- insta_posts(query = "francediplo", 
                         scope = "username",
                         max_posts = 3, 
                         scrape_comments = T)

francediplo_comments
```

## Save output to csv

As function scrapes, the data is saved and continously appended to a `.csv` file (for when you have long scraping tasks). Just specify a path for the `save_path` argument.

```{r, eval = F}
francediplo <- insta_posts(query = "francediplo", 
                         scope = "username",
                         max_posts = 5, 
                         scrape_comments = F, 
                         save_path = "./francediplo.csv")

readr::read_csv("./francediplo.csv")

# Remove file
unlink("./francediplo.csv")
```


## Get User or Hashtag posts in specific timerange

Just specify both an argument for `since` (latest date) and `until` (earliest date) and get Instagram posts in specific timerange.

```{r, eval = F}
soeder <- insta_posts(query = "markus.soeder",
                         scope = "username",
                         max_posts = 20,
                         scrape_comments = F,
                         since = "2024-06-15",
                         until = "2024-06-20"
                      )
soeder

```

## Login with your Instagram account

Some functionalities (like scraping followers from an account) are only available if you login with your Instagram account. For this purpose, `instar` functions will read from your environment variables. 



In order to add the info to your environment file, you can use the function `edit_r_environ()` from the [`usethis` package](https://usethis.r-lib.org/).

```{r, eval = F}
usethis::edit_r_environ()
```


This will open your .Renviron file in your text editor. Now, you can add the following line(s) to it:

```{r, eval = F}
INSTAGRAM_LOGIN=YOUR_USERNAME
INSTAGRAM_PW=YOUR_PW
```

Save the file and restart R for the changes to take effect.

The password line is optional and can also be provided via a prompt which will appear if you run `insta_login` without specifying the `passwd` argument (if you are icky about typing out your password which you should always be).

Now you can use `insta_login` in the following way:

```{r, eval=F}
insta_login(save = T)
```

`save = T` will save your credentials, so next time you can just do `load = T` and you don't need to specify your password again:

```{r, eval=F}
insta_login(load = T)
```


